### 2023-04-12 reachable-resilience.tex
details

\begin{theorem}\label{downward srp}
{\sc state-resilience} is decidable for ideal effective WSTS with downward compatibility,\alain{a-t-on aussi la upward compatibility ?}
\mathieu{oui}
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}

>>>>

\begin{theorem}\label{downward srp}
{\sc state-resilience} is decidable for ideal effective WSTS with downward and upward compatibilities,
%\alain{a-t-on aussi la upward compatibility ?}
%\mathieu{oui}
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}
